FIN 416 Tables

### 2025-03-20 416 Tables, Nearly done.qmd
Fixed Data

@@

spy_monthly_returns <- spy_data %>%
  tq_transmute(select = adjusted, 
               mutate_fun = periodReturn, 
               period = "monthly", 
               type = "log") %>% 
  mutate(SPY.RETURNS = monthly.returns)

@@

```{r}

BenchIVOL_df <- read.csv("https://raw.githubusercontent.com/boykowealth/TailRiskPremium_PortfolioConcept/refs/heads/main/Portfolios_Formed_on_RESVAR.csv")

@@

@@

slide23_data <- slide23_data %>% 
  summarise(
    across(c(New, Base,SPY.RETURNS, rf.rate ), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(Base, New, use = "complete.obs")
  )

>>>>

library(dplyr)
library(tidyr)

@@

spy_monthly_returns <- spy_data %>%
  tq_transmute(select = adjusted, 
               mutate_fun = periodReturn, 
               period = "monthly", 
               type = "log") %>% 
  mutate(SPY.RETURNS = monthly.returns)
```

@@

```{}
```

@@

##
BenchIVOL_df <- read.csv("FINAL_NOT_SUCKY.csv", colClasses = c("date" = "character")) %>% 
  mutate(date = as.Date(zoo::as.yearmon(date, "%Y%m"), frac = 1),
         hi20 = hi20 / 100,
         lo20 = lo20 / 100,
         fammaPort = (hi20 + lo20) / 2
         ) %>% 
  dplyr::select(date, fammaPort)

##

@@

slide23_data <- slide23_data %>% 
  dplyr::left_join(BenchIVOL_df, by = "date")

slide23_data <- slide23_data %>% 
  summarise(
    across(c(New, Base, fammaPort, SPY.RETURNS, rf.rate), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(Base, New, use = "complete.obs")
  )
